MG7: Configurable and scalable 16S data analysis

### 2016-07-26 docs/mg7-paper/out/paper.tex
reword best hits to valid hits

All the assignment procedures work by default with input the set of
BLAST hits which have maximum bitscore among those covering the whole
query sequence; we will call this the set of best hits of a query. Note
that the criteria which determines this set of best hits is fully
configurable, adjusted to conform to its meaning in each particular
dataset: those hits which we should take into account as valid for
assignment. This is of course experiment-dependent, and we can account
for read quality or technology-specific error profiles through
configuring these criteria for the set of best hits.

@@

The LCA assignment simply computes the lowest common ancestor of the set
of best hits. Other metagenomics analysis approaches
\citep{huson2012microbial} have adopted LCA-based assignment algorithms,
as it provides the most precise assignment for a set of taxa, with no
further information available\footnote{the lowest common ancestor of a
  set of nodes in a tree is just their product in the tree viewed as a
  poset, with the ``parent of'' partial order}; as our reference
database is already heavily preprocessed and checked for internal
consistency, there is no need for altering the lowest common ancestor in
any way, as is customarily done in other cases.

>>>>

All the assignment procedures work by default with input the set of
BLAST hits which have maximum bitscore among those covering the whole
query sequence; we will call this the set of valid hits of a query. Note
that the criteria which determines this set of valid hits is fully
configurable, and should be adjusted to conform to its meaning in each
particular dataset: those hits which we should take into account as
valid for assignment. This is of course experiment-dependent, and the
criteria for valid hits should account for read quality or
technology-specific error profiles.

@@

The LCA assignment simply computes the lowest common ancestor of the set
of valid hits. Other metagenomics analysis approaches
\citep{huson2012microbial} have adopted LCA-based assignment algorithms,
as it provides the most precise assignment for a set of taxa, with no
further information available\footnote{the lowest common ancestor of a
  set of nodes in a tree is just their product in the tree viewed as a
  poset, with the ``parent of'' partial order}; as our reference
database is already heavily preprocessed and checked for internal
consistency, there is no need for altering the lowest common ancestor in
any way, as is customarily done in other cases. MG7 operates under the
assumption that hits which fulfill the user-defined criteria for being
valid hits should be treated on an equal footing, and in that case
taking their LCA is the coherent assignment choice with minimum
information loss.
